Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-17 paper/paper.Rmd
violin

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)
library(tidyverse)
library(purrr)
library(lvplot)

@@

```{r timeData}
times <- amin %>% 
  filter(type!="Manual") %>% 
  select(file, type, time.user.self, time.sys.self) %>% 
  group_by(file, type) %>% 
  mutate(n=n(), time.user.self=first(time.user.self), time.sys.self=first(time.sys.self))
```

@@

# violin plot
t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self, fill=type)) +
  geom_violin(scale = "count", alpha=0.5, adjust=0.01) + ylim(0,0.08) +
  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
  facet_wrap(~ type) +
  xlab("Amount of faces found") +
  ylab("Time taken per image (Seconds)") + scale_fill_manual("", values=type.colours) +
  geom_smooth(aes(x=n, time.sys.self), method="lm", se=F, colour="black") + 
  scale_colour_manual("", values=type.colours)

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)
library(gridExtra)
library(ggmosaic)
library(tidyverse)
library(purrr)

@@

```{r timeData}
times <- amin %>% 
  filter(type!="Manual") %>% 
  select(file, type, time.user.self, time.sys.self) %>% 
  group_by(file, type) %>% 
  mutate(n=n()) %>% 
  distinct() %>% ungroup()
```

@@

# violin plot
t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self, fill=type)) +
  geom_violin(scale = "width", alpha=0.5) + ylim(0,0.08) +
  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
  facet_wrap(~ type) +
  xlab("Amount of faces found") +
  ylab("Time taken per image (Seconds)") + scale_fill_manual("", values=type.colours) +
  geom_smooth(aes(x=n, time.sys.self), method="lm", se=F, colour="black") + 
  scale_colour_manual("", values=type.colours)
